---
title: "0.KCCQ_associations"
format: html
editor: visual
---

```{r}
#| warning: false
#| include: false

library(here)
source(here::here("R/1_data_management/prep_library.R"))
source(here::here("R/functions/functions.R"))
source(here::here("R/1_data_management/1_load_data.R"))
```

# Association between KCCQ and cardiac function

```{r}
#| include: false
#| 
 # study_data %>% 
 #     dplyr::select(
 # mvdectimems,
 # eepsept,
 # mvea,
 # glpsavgafi,
 # lvdmassindexgm,
 # laesvialmlm,
 # lvefautoefbip,
 # lvef4dautolvq)  %>%
 #     hist.data.frame() 
```

```{r}
#| include: false

echo_measures <- c("mvecms",
                   "eepsept",
                   "mvea",
                   "glpsavgafi",
                   "lvdmassindexgm",
                   "laesvialmlm",
                   "lvef4dautolvq")

results_hf_symptoms <- map(echo_measures, ~ lm_function(study_data, .x, "hf_symptoms")) %>% 
    list_rbind()

results_hf_symptoms %>% 
    knitr::kable()
```

*Hypothesis: Higher KCCQ-SCORE are associated with better cardiac function outcomes*

## E prime

```{r}
#| include: false


E_prime_results <- study_data_long %>% 
    dplyr::select(kccq, kccq_domain, mvecms, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), mvecms) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate()

E_prime_results %>% 
    plot_estimates() + 
    xlab("e' per SD higher KCCQ-score")

E_prime_outcome <- E_prime_results %>% 
    select(kccq,estimate, conf.low, conf.high, p.value) %>% 
    mutate(outcome = "E'") %>% 
    filter(!c(kccq== str_detect(kccq,"Q")))
    
```

```{r}
#| echo: false

study_data_long %>% 
    dplyr::select(kccq, kccq_domain, mvecms, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), mvecms) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate_overall() %>% 
    plot_estimates_overall() + 
    xlab("e' per 1 higher KCCQ-score")
```

Higher e' higher cardiac function

## E/e'

```{r}
#| include: false

E_E_prime_results <- study_data_long %>% 
    dplyr::select(kccq, kccq_domain, eepsept, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), eepsept) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate()

E_E_prime_outcome <- E_E_prime_results %>% 
    select(kccq,estimate, conf.low, conf.high, p.value) %>% 
    mutate(outcome = "E/e'") %>% 
    filter(!c(kccq== str_detect(kccq,"Q")))

```

```{r}
#| echo: false

    study_data_long %>% 
    dplyr::select(kccq, kccq_domain, eepsept, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), eepsept) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate_overall() %>% 
    plot_estimates_overall() + 
    xlab("e' per 1 higher KCCQ-score")
```

LAE_lf_art_enlarg, LVH_lf_vent_hyptro, DD_dia_dys, GLS_imparied, GLS_abnormal Lower E/e' higher cardiac function

## E/A ratio

```{r}
#| include: false

E_A_ratio_results <- study_data_long %>% 
    dplyr::select(kccq, kccq_domain, mvea, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), mvea) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate()

E_A_ratio_otcome <- E_A_ratio_results %>% 
    select(kccq,estimate, conf.low, conf.high, p.value) %>% 
    mutate(outcome = "E/A") %>% 
    filter(!c(kccq== str_detect(kccq,"Q")))
```

```{r}
#| echo: false

study_data_long %>% 
    dplyr::select(kccq, kccq_domain, mvea, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), mvea) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate_overall() %>% 
    plot_estimates_overall() + 
    xlab("E/A per 1 higher KCCQ-score")
```

Higher E/A better cardiac function

## GLS ratio

```{r}
#| include: false

GLS_ratio_results <- study_data_long %>% 
    dplyr::select(kccq, kccq_domain, glpsavgafi, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), glpsavgafi) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate()

GLS_ratio_outcome <- GLS_ratio_results %>% 
    select(kccq,estimate, conf.low, conf.high, p.value) %>% 
    mutate(outcome = "GLS Ratio") %>% 
    filter(!c(kccq== str_detect(kccq,"Q")))
```

```{r}
#| echo: false

study_data_long %>% 
    dplyr::select(kccq, kccq_domain, glpsavgafi, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), glpsavgafi) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate_overall() %>% 
    plot_estimates_overall() + 
    xlab("GLS per 1 higher KCCQ-score")

```

Lower GLS higher cardiac function

## Left ventricular mass index

```{r}
#| include: false

LVMass_results <- study_data_long %>% 
    dplyr::select(kccq, kccq_domain, lvdmassindexgm, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), lvdmassindexgm) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate()

LVMass_outcome <- LVMass_results %>% 
    select(kccq,estimate, conf.low, conf.high, p.value) %>% 
    mutate(outcome = "Left ventricular mass index") %>% 
    filter(!c(kccq== str_detect(kccq,"Q")))
```

```{r}
#| echo: false
study_data_long %>% 
    dplyr::select(kccq, kccq_domain, lvdmassindexgm, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), lvdmassindexgm) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate_overall() %>% 
    plot_estimates_overall() + 
    xlab("LVMi 1 higher KCCQ-score")

```

Lower LVMi higher cardiac function

## Lef atrium volume

```{r}
#| include: false

LVAv_results <- study_data_long %>% 
    dplyr::select(kccq, kccq_domain, laesvialmlm, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), laesvialmlm) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate()

LVAv_outcome <- LVAv_results %>% 
    select(kccq,estimate, conf.low, conf.high, p.value, p.value) %>% 
    mutate(outcome = "Left ventricular atrium volume") %>% 
    filter(!c(kccq== str_detect(kccq,"Q")))
```

```{r}
#| echo: false

study_data_long %>% 
    dplyr::select(kccq, kccq_domain, laesvialmlm, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), laesvialmlm) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate_overall() %>% 
    plot_estimates_overall() + 
    xlab("LAV per 1 higher KCCQ-score")

```

## Left ejection fraction

```{r}
#| include: false

LEF_results <- study_data_long %>% 
    dplyr::select(kccq, kccq_domain, lvef4dautolvq, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), lvef4dautolvq) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate()

LEF_outcome <- LEF_results %>% 
    select(kccq,estimate, conf.low, conf.high, p.value) %>% 
    mutate(outcome = "Left ejection fraction") %>% 
    filter(!c(kccq== str_detect(kccq,"Q")))

```

```{r}
#| echo: false

study_data_long %>% 
    dplyr::select(kccq, kccq_domain, lvef4dautolvq, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), lvef4dautolvq) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate_overall() %>% 
    plot_estimates_overall() + 
    xlab("LEF per 1 higher KCCQ-score")

```

Higher EF higher cardiac function

```{r}
#| echo: false
#| 
results_kccq_echo <- rbind(E_prime_outcome,
E_E_prime_outcome,
E_A_ratio_otcome,
GLS_ratio_outcome,
LVMass_outcome,
LVAv_outcome,
LEF_outcome)

results_kccq_echo %>%
    ggplot(aes(x = outcome  , y = fct_inorder(kccq), fill = p.value)) +
    geom_tile() +
    scale_fill_gradient(low = "white", high = "red") +
    labs(x = "Subtypes of heart failure", y = "KCCQ domains", title = "Estimate  (95% CI) per 10 higher in KCCQ-domain ")+
    geom_text(aes(label = paste0(round(estimate*10,2)," (",round(conf.low*10,2),"; ", round(conf.high*10,2),")")),
                  color = "black", size = 3)+
    scale_fill_distiller(direction = -1,
                         limits = c(min(results_kccq_echo$p.value), max(results_kccq_echo$p.value)))
```

Higher e' higher cardiac function Higher E/A better cardiac function Lower GLS higher cardiac function Lower LVMi higher cardiac function Higher EF higher cardiac function

# Part conclusion

Higher KCCQ score indicates better cardiac systolic function. However, indications of diastolic dysfunction was only observed for left atrium volume.

# Classified heart failure association

```{r}
#| include: false

#hf_diagnosis <- c("LAE_lf_art_enlarg","LVH_lf_vent_hyptro", "GLS_imparied",  "DD_dia_dys", "EF_HF", "HFpEF", "HFmrEF_rEF")
```

```{r}
#| include: false
#| message: false
#| warning: false
# 
# 
# loop_it <- function(hf_outcome, data) {
# 
# data %>% 
#     dplyr::select(kccq, kccq_domain, hf_outcome, gender, age,
#                   record_id) %>% 
#     tidyr::drop_na() %>%
#     dplyr::rename_with(~ paste0("echo_",.), paste0(hf_outcome)) %>%
#     calculate_estimates_or() %>%
#     arrange_and_exponetiate() %>%
#     dplyr::rename(nobs = last_col()) %>% 
#     plot_estimates_or() +
#     xlab(paste0(hf_outcome ,"per SD higher KCCQ-score"))
# 
# }
# 
# map(hf_diagnosis, ~loop_it(.x, study_data_long))


# test<- study_data_long %>% 
#     dplyr::select(kccq, kccq_domain, "DD_dia_dys", gender, age,
#                   record_id) %>% 
#     tidyr::drop_na() %>%
#     dplyr::rename_with(~ paste0("echo_",.), paste0("DD_dia_dys")) %>% 
#     dplyr::mutate(echo_DD_dia_dys = factor(echo_DD_dia_dys),
#                     gender = as.factor(gender))
# 
# 
# table(study_data$gender, study_data$DD_dia_dys)
# str(test)
# test2 <- test %>%
#     calculate_estimates_or() %>%
#     arrange_and_exponetiate() %>% 
#     dplyr::rename(nobs = last_col())%>%
#     plot_estimates_or() +
#     xlab(paste0("LVH_lf_vent_hyptro" ,"per SD higher KCCQ-score"))

```
