---
title: "0.KCCQ_associations"
format: pdf
editor: visual
---

```{r}
#| warning: false
#| include: false

library(here)
source(here::here("R/1_data_management/prep_library.R"))
source(here::here("R/functions/functions.R"))
source(here::here("R/1_data_management/1_load_data.R"))
```

# Association between KCCQ and cardiac function

```{r}
#| echo: false
#| 
  study_data_complete %>%
      dplyr::select(
                "mveesept",
                   "lvmi",
                   "lavi",
                   "gls_av")  %>%
      hist.data.frame()
```

```{r}
#| include: false

echo_measures <- c("mveesept",
                   "lvmi",
                   "lavi",
                   "gls_av")

results_hf_symptoms <- map(echo_measures, ~ lm_function(study_data_complete, .x, "hf_symptoms")) %>% 
    list_rbind()

results_hf_symptoms %>% 
    knitr::kable()
```

*Hypothesis: Higher KCCQ-SCORE are associated with better cardiac function outcomes*

## E prime

```{r}
#| include: false

E_prime_results <- study_data_long %>% 
    dplyr::select(kccq, kccq_domain, mveesept, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), mveesept) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate()

E_prime_results %>% 
    plot_estimates() + 
    xlab("e' per SD higher KCCQ-score")

E_prime_outcome <- E_prime_results %>% 
    select(kccq,estimate, conf.low, conf.high, p.value) %>% 
    mutate(outcome = "E'") %>% 
    filter(!c(kccq== str_detect(kccq,"Q")))
    
```

```{r}
#| echo: false

study_data_long %>% 
    dplyr::select(kccq, kccq_domain, mveesept, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), mveesept) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate_overall() %>% 
    plot_estimates_overall() + 
    xlab("e' per 1 higher KCCQ-score")
```

Higher e' higher cardiac function

## GLS ratio

```{r}
#| include: false

GLS_ratio_results <- study_data_long %>% 
    dplyr::select(kccq, kccq_domain, gls_av, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), gls_av) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate()

GLS_ratio_outcome <- GLS_ratio_results %>% 
    select(kccq,estimate, conf.low, conf.high, p.value) %>% 
    mutate(outcome = "GLS Ratio") %>% 
    filter(!c(kccq== str_detect(kccq,"Q")))
```

```{r}
#| echo: false

study_data_long %>% 
    dplyr::select(kccq, kccq_domain, gls_av, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), gls_av) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate_overall() %>% 
    plot_estimates_overall() + 
    xlab("GLS per 1 higher KCCQ-score")

```

Lower GLS higher cardiac function

## Left ventricular mass index

```{r}
#| include: false

LVMass_results <- study_data_long %>% 
    dplyr::select(kccq, kccq_domain, lvmi, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), lvmi) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate()

LVMass_outcome <- LVMass_results %>% 
    select(kccq,estimate, conf.low, conf.high, p.value) %>% 
    mutate(outcome = "Left ventricular mass index") %>% 
    filter(!c(kccq== str_detect(kccq,"Q")))
```

```{r}
#| echo: false
study_data_long %>% 
    dplyr::select(kccq, kccq_domain, lvmi, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), lvmi) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate_overall() %>% 
    plot_estimates_overall() + 
    xlab("LVMi 1 higher KCCQ-score")

```

Lower LVMi higher cardiac function

## Lef atrium volume

```{r}
#| include: false

LVAv_results <- study_data_long %>% 
    dplyr::select(kccq, kccq_domain, lavi, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), lavi) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate()

LVAv_outcome <- LVAv_results %>% 
    select(kccq,estimate, conf.low, conf.high, p.value, p.value) %>% 
    mutate(outcome = "Left ventricular atrium volume") %>% 
    filter(!c(kccq== str_detect(kccq,"Q")))
```

```{r}
#| echo: false

study_data_long %>% 
    dplyr::select(kccq, kccq_domain, lavi, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), lavi) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate_overall() %>% 
    plot_estimates_overall() + 
    xlab("LAV per 1 higher KCCQ-score")

```

<!-- ## Left ejection fraction -->

<!-- ```{r} -->

<!-- #| include: false -->

<!-- LEF_results <- study_data_long %>%  -->

<!--     dplyr::select(kccq, kccq_domain, lvef4dautolvq, gender, age, -->

<!--                   record_id) %>%  -->

<!--     tidyr::drop_na() %>%  -->

<!--     dplyr::rename_with(~ paste0("echo_",.), lvef4dautolvq) %>%  -->

<!--     calculate_estimates() %>%  -->

<!--     arrange_and_exponetiate() -->

<!-- LEF_outcome <- LEF_results %>%  -->

<!--     select(kccq,estimate, conf.low, conf.high, p.value) %>%  -->

<!--     mutate(outcome = "Left ejection fraction") %>%  -->

<!--     filter(!c(kccq== str_detect(kccq,"Q"))) -->

<!-- ``` -->

<!-- ```{r} -->

<!-- #| echo: false -->

<!-- study_data_long %>%  -->

<!--     dplyr::select(kccq, kccq_domain, lvef4dautolvq, gender, age, -->

<!--                   record_id) %>%  -->

<!--     tidyr::drop_na() %>%  -->

<!--     dplyr::rename_with(~ paste0("echo_",.), lvef4dautolvq) %>%  -->

<!--     calculate_estimates() %>%  -->

<!--     arrange_and_exponetiate_overall() %>%  -->

<!--     plot_estimates_overall() +  -->

<!--     xlab("LEF per 1 higher KCCQ-score") -->

<!-- ``` -->

```{r}
#| echo: false
#| 
results_kccq_echo <- rbind(
E_prime_outcome,
# E_E_prime_outcome,
# E_A_ratio_otcome,
GLS_ratio_outcome,
LVMass_outcome,
LVAv_outcome
#LEF_outcome
)

results_kccq_echo %>%
    ggplot(aes(x = outcome, y = fct_inorder(kccq), fill = p.value)) +
    geom_tile() +
    scale_fill_gradient(low = "red", high = "white", 
                        limits = c(0, 0.20), 
                        oob = scales::squish) +
    labs(x = "Subtypes of heart failure", y = "KCCQ domains", title = "Estimate (95% CI) per 10 higher in KCCQ-domain") +
    geom_text(aes(label = paste0(round(estimate*10, 2), " (", round(conf.low*10, 2), "; ", round(conf.high*10, 2), ")")),
              color = "black", size = 3) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))

```

```{r}
#| echo: false
results_kccq_echo$kccq

results_kccq_echo %>% 
    filter(kccq %in% c("Physical_Limitation_Score", "Symptom_Frequency_Score", "Quality_Life_Score", "Social_Limitation_Score", "Clinical_Summary_Score", "Overall_Summary_Score")) %>% 
 ggplot(aes(x = outcome, y = kccq, fill = p.value)) +
    geom_tile() +
    scale_fill_gradient(low = "red", high = "white", 
                        limits = c(0, 0.20), 
                        oob = scales::squish) +
    labs(x = "Subtypes of heart failure", y = "KCCQ domains", title = "HF subtype value in SD (95% CI) per 10 higher in KCCQ-domain") +
    geom_text(aes(label = paste0(round(estimate*10, 2), " (", round(conf.low*10, 2), "; ", round(conf.high*10, 2), ")")),
              color = "black", size = 3) +
  theme(axis.text.x = element_text(angle = 30, hjust = 1))
```

Higher e' higher cardiac function Higher E/A better cardiac function Lower GLS higher cardiac function Lower LVMi higher cardiac function Higher EF higher cardiac function

# Part conclusion

Higher KCCQ score indicates better cardiac systolic function. However, indications of diastolic dysfunction was only observed for left atrium volume.
