---
title: "analysis_dichotomized"
format: html
editor: visual
---

---
title: "Analysis"
format: pdf
editor: visual
---

```{r}
study_data_long_dicho <- study_data_complete %>%
    rename_with(~ paste0("t_kccq_", .),
                c(Physical_Limitation_Score, Symptom_Frequency_Score, Quality_Life_Score,
                  Social_Limitation_Score, Overall_Summary_Score, Clinical_Summary_Score)) %>%
    rename_with(~ paste0("t_kccq_", .), ends_with("rescaled")) %>%
    mutate(across(starts_with("t_kccq_"),
                  ~ factor(ifelse(. < 90, "low", "high"), levels = c("low", "high")))) %>%
    df_kccq_long_format()
```

# table 1

```{r}
study_data %>% 
    dplyr::select("hf_symptoms",
                  
                  Physical_Limitation_Score, Symptom_Frequency_Score, Quality_Life_Score, Social_Limitation_Score, Overall_Summary_Score, Clinical_Summary_Score,
                  age, age_current, gender, year_diag_diab, age_dm_diag, education,
smoking, "days_alcohol","days_alcohol_cov",
"height", "weight","bmi",
hdl, chol,"hdl_cat", ldl, trig,
a1c_pcent, a1c_mmol, glucosef,
bp_syst_mean, bp_diast_mean, waist_1, hip_1,
heart_rate, heart_rate2 ,heart_rate3,
                  
                  "LAE_lf_art_enlarg", "GLS_imparied", "LVH_lf_vent_hyptro", "DD_dia_dys", "EF_HF", "HFpEF", "HFmrEF_rEF") %>%
    gtsummary::tbl_summary(by = "hf_symptoms")
```

# Association between KCCQ and cardiac function

```{r}
#| include: false
#| 
 # study_data %>% 
 #     dplyr::select(
 # mvdectimems,
 # eepsept,
 # mvea,
 # glpsavgafi,
 # lvdmassindexgm,
 # laesvialmlm,
 # lvefautoefbip,
 # lvef4dautolvq)  %>%
 #     hist.data.frame() 
``` 

```{r}

echo_measures <- c("mvecms",
                   "eepsept",
                   "mvea",
                   "glpsavgafi",
                   "lvdmassindexgm",
                   "laesvialmlm",
                   "lvef4dautolvq")

results_hf_symptoms <- map(echo_measures, ~ lm_function(study_data, .x, "hf_symptoms")) %>% 
    list_rbind()

results_hf_symptoms %>% 
    knitr::kable()
```


*Hypothesis: Higher KCCQ-SCORE are associated with better cardiac function outcomes*

## E prime

```{r}
#| echo: false

study_data_long_dicho %>% 
    dplyr::select(kccq, kccq_domain, mvecms, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), mvecms) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate() %>% 
    plot_estimates() + 
    xlab("e' per SD higher KCCQ-score")

```

Higher e' higher cardiac function


## E/e'

```{r}
#| echo: false

study_data_long_dicho %>% 
    dplyr::select(kccq, kccq_domain, eepsept, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), eepsept) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate() %>% 
    plot_estimates() + 
    xlab(" E/e' per SD higher KCCQ-score")

```


LAE_lf_art_enlarg, LVH_lf_vent_hyptro, DD_dia_dys, GLS_imparied, GLS_abnormal
Lower E/e' higher cardiac function

## E/A ratio

```{r}
#| echo: false

study_data_long_dicho %>% 
    dplyr::select(kccq, kccq_domain, mvea, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), mvea) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate() %>% 
    plot_estimates() + 
    xlab("E/A per SD higher KCCQ-score")

```



Higher E/A better cardiac function

## GLS ratio

```{r}
#| echo: false

study_data_long_dicho %>% 
    dplyr::select(kccq, kccq_domain, glpsavgafi, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), glpsavgafi) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate() %>% 
    plot_estimates() + 
    xlab("GLS per SD higher KCCQ-score")

```


Lower GLS higher cardiac function

## Left ventricular mass index

```{r}
#| echo: false

study_data_long_dicho %>% 
    dplyr::select(kccq, kccq_domain, lvdmassindexgm, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), lvdmassindexgm) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate() %>% 
    plot_estimates() + 
    xlab("LVMi SD higher KCCQ-score")

```



Lower LVMi higher cardiac function



## Lef atrium volume

```{r}
#| echo: false

study_data_long_dicho %>% 
    dplyr::select(kccq, kccq_domain, laesvialmlm, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), laesvialmlm) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate() %>% 
    plot_estimates() + 
    xlab("LAV per SD higher KCCQ-score")

```


## Left ejection fraction

```{r}
#| echo: false

study_data_long_dicho %>% 
    dplyr::select(kccq, kccq_domain, lvef4dautolvq, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>% 
    dplyr::rename_with(~ paste0("echo_",.), lvef4dautolvq) %>% 
    calculate_estimates() %>% 
    arrange_and_exponetiate() %>% 
    plot_estimates() + 
    xlab("LEF per SD higher KCCQ-score")

```



Higher EF higher cardiac function

# Part conclusion

Higher KCCQ score indicates better cardiac systolic function. However, indications of diastolic dysfunction was only observed for left atrium volume.

# Classified heart failure association

```{r}
hf_diagnosis <- c("LAE_lf_art_enlarg","LVH_lf_vent_hyptro", "GLS_imparied",  "DD_dia_dys", "EF_HF", "HFpEF", "HFmrEF_rEF")
```

```{r}
#| echo: false
#| message: false
#| warning: false


loop_it <- function(hf_outcome, data) {

data %>% 
    dplyr::select(kccq, kccq_domain, hf_outcome, gender, age,
                  record_id) %>% 
    tidyr::drop_na() %>%
    dplyr::rename_with(~ paste0("echo_",.), paste0(hf_outcome)) %>%
    calculate_estimates_or() %>%
    arrange_and_exponetiate() %>%
    dplyr::rename(nobs = last_col()) %>% 
    plot_estimates_or() +
    xlab(paste0(hf_outcome ,"per SD higher KCCQ-score"))

}

map(hf_diagnosis, ~loop_it(.x, study_data_long_dicho))


# test<- study_data_long_dicho %>% 
#     dplyr::select(kccq, kccq_domain, "DD_dia_dys", gender, age,
#                   record_id) %>% 
#     tidyr::drop_na() %>%
#     dplyr::rename_with(~ paste0("echo_",.), paste0("DD_dia_dys")) %>% 
#     dplyr::mutate(echo_DD_dia_dys = factor(echo_DD_dia_dys),
#                     gender = as.factor(gender))
# 
# 
# table(study_data$gender, study_data$DD_dia_dys)
# str(test)
# test2 <- test %>%
#     calculate_estimates_or() %>%
#     arrange_and_exponetiate() %>% 
#     dplyr::rename(nobs = last_col())%>%
#     plot_estimates_or() +
#     xlab(paste0("LVH_lf_vent_hyptro" ,"per SD higher KCCQ-score"))

```


